Badges

### 2024-11-20 pages/badges.qmd
chore(badges): minor tweak to wording

| Criteria | ACM Artifacts Available | NISO ORO | NISO ORO-A | COS Open Code | IEEE Code Available |
| - | - | - | - | - | - |
| Artefacts are archived in a repository that is: (a) public (b) guarantees persistence (c) gives a unique identifier (e.g. DOI) | ✅ | ✅ | ✅ | ✅ | ❌ |
| Open licence | ❌ | ✅ | ✅ | ✅ | ❌ |
| Complete (all relevant artefacts are available) | ❌ | ❌ | ✅ | ❌ | ✅ |
| Sufficient explanation to "understand how the code is used and relates to the reported methodology, including information about versions of software, systems, and packages." | ❌ | ❌ | ❌ | ✅ | ❌ |
: {tbl-colwidths="[50, 10, 10, 10, 10, 10]"}

@@

| Criteria | ACM Artifacts Evaluated - Functional | ACM Artifacts Evaluated - Reusable | IEEE Code Reviewed |
| - | - | - | - |
| Documentation with: (a) inventory of artefacts (b) sufficient description for artefacts to be exercised | ✅ | ✅ | ❌ |
| Artefacts relevant to paper | ✅ | ✅ | ❌ |
| Complete (all relevant artefacts are available) | ✅ | ✅ | ✅ |
| Scripts can be executed | ✅ | ✅ | ✅ |
| Artefacts are "carefully documented and well-structured to the extent that reuse and repurposing is facilitated", adhering to norms and standards | ❌ | ✅ | ❌ |
: {tbl-colwidths="[50, 16.66, 16.66, 16.66]"}

>>>>

| Criteria | ACM Artifacts Available | NISO ORO | NISO ORO-A | COS Open Code | IEEE Code Available |
| - | - | - | - | - | - |
| Artefacts are archived in a repository that is: (a) public (b) guarantees persistence (c) gives a unique identifier (e.g. DOI) | ✅ | ✅ | ✅ | ✅ | ❌ |
| Open licence | ❌ | ✅ | ✅ | ✅ | ❌ |
| Complete (all artefacts that would be needed for reproduction) | ❌ | ❌ | ✅ | ❌ | ✅ |
| Documents (a) how code is used (b) how it relates to article (c) software, systems, packages and versions | ❌ | ❌ | ❌ | ✅ | ❌ |
: {tbl-colwidths="[50, 10, 10, 10, 10, 10]"}

@@

| Criteria | ACM Artifacts Evaluated - Functional | ACM Artifacts Evaluated - Reusable | IEEE Code Reviewed |
| - | - | - | - |
| Documents (a) inventory of artefacts (b) sufficient description for artefacts to be exercised | ✅ | ✅ | ❌ |
| Artefacts relevant to paper | ✅ | ✅ | ❌ |
| Complete (all artefacts that would be needed for reproduction) | ✅ | ✅ | ✅ |
| Scripts can be successfully executed | ✅ | ✅ | ✅ |
| Artefacts are "carefully documented and well-structured to the extent that reuse and repurposing is facilitated", adhering to norms and standards | ❌ | ✅ | ❌ |
: {tbl-colwidths="[50, 16.66, 16.66, 16.66]"}
